---
title: "Group10_final_presentation"
output: ioslides_presentation
date: '2022-05-02'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.



## Introduction to the project
-Sensory evolution of hearing in tettigoniids with differing
communication systems
- In TettigoniSensory evolution of hearing in tettigoniids with differing
communication systemsidae,hearing organs are essential in mate detection(Unidirectional/bidirectional)
- Poecilimon(genus) and their evolution from bidirectional to unidirectional
-Recreating plots from the article

## Materials and methods
- Characteristics of the auditory system for functional adaptations analysed:
  (i) Dimension of sound-receiving structures
  (ii) Number of auditory sensilla
  (iii) Hearing sensitivity
- Fifteen species selected for morphometric analysis of auditory structures
- Neuroanatomy and hearing sensitivity investigated in subset of five selected species
- Animals collected at locations in Greece, Slovenia and the Czech Republic 
- Specimens for anatomical measurements collected between 1994 and 1996 and stored in ethanol
- Specimens for neuroanatomical and physiological experiments collected in May/June 2011 and June 2012

## {data-background=graph.jpeg data-background-size=center}

## Dataset, choice and considerations
- Messy dataset,missing data and non tidy format
- Datasets considered
 (i) Measurements for the different crickets
 (ii) Measurements for auditory threshold
- Lack of consistent ID's making merging of datasets impossible
- Units in database 2
- Tricky metadata
-joining metadata to gain new insights


## Workflow of the project

## Graphs

## Results
- Spiracle size was correlated with the communication system of the respective species and showed clustering into discrete groups
- The tympana scale with body size , whereas the spiracles differ between uni- and bidirectional acoustically communicating species and between sexes.
- In species with unidirectional communication, the spiracles are much smaller than the
tympana, both in the P. propinquus group and especially in the P. ampliatus group.
- The sensilla number is highest in the three
bidirectional communicating Poecilimon species and the bidirectional out-group species I. modestior
- Although the sexes within a
species were similar, auditory sensitivity differed clearly
between species
-  Representatives of those species with large spiracles (P. ornatus, I. modestior) have
the highest sensitivity
- In P. ampliatus, a representative of a
unidirectional communicating species with small acoustic spiracles, hearing thresholds are rather high, mainly
above 50 dB SPL.
-
## Discussion
- the greatest differences exist between bidirectional and unidirectional communicating species regardless of song characters.
-  Can be assumed that overall body size might be the evolutionary target, if tympanal structures come under positive selection
- Tympana are important structures for sound perception in Tettigoniidae, and neither the acoustic communication system nor sex greatly affects their size.
- Limitations and drawbacks of the plots from the paper
-Alternative representation of the plot(morphological comparison plot)

##Challenges faced
-Loading the script-merging multiple datasets from 1 excel sheet
-Recreating morphometric plots by recognizing the general patterns of the plots
-Removed unexplainable data (e.g. rows in meta data with "ex Stumpner & Heller, 1992")
-lack of consistant ID makes reproducibility difficult
 
## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

